### 2015-04-12 abstract.tex
Adding updated (slightly) bib, adding updates to intro and related work.
Adding review and moving stuff.
Added Floating surface recon
Adding refs to optimal lattice stuff in 2d.
Cleaned up refs/sec refs/symbols up to approach.

In this work, we cast the well-known Poisson surface reconstruction algorithm into a more general setting, we reformulate it in terms of shift invariant spaces (spaces that are spanned by lattice translates of an admissible generating function). The treatment is general, but our specific interest is in reconstructing a surface of a solid model from an oriented point-set within function spaces defined over the body centred cubic lattice. We also propose a general framework for approximating the solution to Poisson?s equation in a hypercube with zero Dirichlet boundary conditions, and a new variational scheme to re-sample the initial oriented point-set onto a regular grid. Once the points have been re-sampled onto a grid, the rest of the pipeline is purely based on digital filtering. We also analyze the error incurred via the digital filtering approximation methodology and propose a Fourier domain error kernel that can be used to design solution filters that fully exploit the approximation capabilities of the target space. Finally, we show that a host of Poisson-like methods fail to take advantage of the full approximation spaces over which they are defined.

%We analyze the error incurred via this approximation methodology and propose a Fourier domain error kernel that can be used to design solution filters that fully exploit the approximation capabilities of the target space and are akin to interpolation and quasi-interpolation filters.

%Our error kernel formulation is validated by conducting numerical experiments on the two dimensional square lattice and the three dimensional Cartesian and body-centered cubic lattices. Additionally, we comment on the equivalence between our method and the finite element method and show how our error kernel formulation can be easily extended to a larger class of differential operators.

%1. Intro:
%Highlight the additional contribution that we formulate a way to solve the Poisson equation on non-Cartesian lattices.

%2. Related work:
%Update references with the work Torsten pointed out and the recent surface reconstruction survey that I mentioned. 
%Cite additional work that talks about the benefits of non-Cartsian lattices (in volume rendering, flow simulation etc.). 
%There are a couple of works that deal with solving Poisson?s equation on non-Cartesian lattices. Please see the attached version of my paper.

%3. Preliminaries:
%Move sections 3.3.1 and 3.3.2 to section 6. Introduce 3.4 earlier.

%4. Approach:
%Expand 4.3 into a new section ? section 5. Move Table 1 to section 6.

%5. Solving Poisson?s Equation.
%This section spells out the details of the filtering methodology for solving Poisson?s equation. I will work on this part. The aim would be to condense the material so that it blends well with the rest of the paper.

%6. Results and Discussion.
%Start by introducing the specific lattices, basis functions, filters used for the experiments (3.3.1, 3.3.2 and table 1 should come here). Additionally, need a subsection here that derives the filter weights for CC and BCC. The rest of the section shows the comparative surface reconstruction experimental results + discussion.

%7. Conclusion.
%Usual mumbo jumbo.

>>>>

In this work, we cast the well-known Poisson surface reconstruction algorithm into a more general setting, we reformulate it in terms of shift invariant spaces (spaces that are spanned by lattice translates of an admissible generating function). The treatment is general, but our specific interest is in reconstructing a surface of a solid model from an oriented point-set within function spaces defined over the body centred cubic lattice. We also propose a general framework for approximating the solution to Poisson's equation in a hypercube with zero Dirichlet boundary conditions, and a new variational scheme to re-sample the initial oriented point-set onto a regular grid. Once the points have been re-sampled onto a grid, the rest of the pipeline is purely based on digital filtering. We also analyze the error incurred via the digital filtering approximation methodology and propose a Fourier domain error kernel that can be used to design solution filters that fully exploit the approximation capabilities of the target space. Finally, we show that a host of Poisson-like methods fail to take advantage of the full approximation spaces over which they are defined.

%%%%
% Todo
%%%%

%5. Indicator funcition:
%Expand

%6. Solving Poisson?s Equation.
%This section spells out the details of the filtering methodology for solving Poisson?s equation. I will work on this part. The aim would be to condense the material so that it blends well with the rest of the paper.

%7. Results and Discussion.
% Additionally, need a subsection here that derives the filter weights for CC and BCC. The rest of the section shows the comparative surface reconstruction experimental results + discussion.

### 2015-04-12 prelim.tex
Cleaned up refs/sec refs/symbols up to approach.

\section{Preliminaries}\label{sec:pois_review}
\subsection{Poisson Surface Reconstruction}
We denote the indicator function of a model $M$ as $$ \chi_M(\mathbf{x}) :=
\begin{cases}
1, & \text{if }\mathbf{x}\text{ is in the interior of the model } M \\
\frac{1}{2}, & \text{if } \mathbf{x}\text{ is on the model's surface}\\
0, & \text{if }\mathbf{x}\text{ is exterior to } M
\end{cases}. $$
The key observation of the Poisson surface reconstruction formulation, is that if one obtains a function $\vec{V}(\mathbf{x})$ with $\vec{V}(\mathbf{x})\approx{\nabla}\chi_M$, that approximates the smoothed gradient of the indicator function, finding an approximation to the indicator function reduces to finding a $\inda$ such that {\small 
\begin{equation} \label{eq:poisson}
	\lapl{\inda} = {\grad} \cdot \vec{V}.
\end{equation}}
We define the set of input surface points to be $P:=\{(\mathbf{p}_1,\mathbf{n}_1), (\mathbf{p}_2,\mathbf{n}_2) \hdots (\mathbf{p}_M,\mathbf{n}_M) : (\mathbf{p}_i,\mathbf{n}_i) \in
\realn^3 \times \realn^3 \}$ where $\mathbf{p}_i$ and $\mathbf{n}_i$ are the position and normal vector of the $i^{th}$ sample respectively. Orientation can be succinctly represented with only two values, however, it is convenient to keep it as the normal at a point, because the length of the normal can be used to encode the sampling density of the point-set at a point. For the following discussion, we also need to introduce the notation $\patch_{\mathbf{s}}$, which denotes a patch of the surface model about the sample location $\mathbf{s}$.

Inspired by the approach of Kazhdan et al.~\cite{Kazhdan06} the approximation $\vec{V}(\vx)$ is defined to be  {\small 
\begin{eqnarray}
	\vec{V}(\vx) & := & \sum_{(\mathbf{s},\mathbf{n}) \in P}\left|\patch_s\right|F(\vx-\mathbf{s})\cdot\vn \label{eq:vdef} \\
	 & \approx & \sum_{(\mathbf{s},\mathbf{n}) \in P} \int_{\patch_s}{F(\mathbf{x} - \mathbf{p}) \nabla \chi (\mathbf{p})} \mathrm{d} \mathbf{p}. \notag  
\end{eqnarray}}
Thus, $\vec{V}(\vx)$ approximates the gradient of the indicator smoothed by some filter $F$, broken up over surface patches of the model. We assume the point sampling to be uniform, thus the area of each patch $\left|\patch_s\right|$ should be a constant, and our resulting approximation will be scaled by an unknown factor. We return to this in \SC{sec:levelset}. The choice of $F$ places computational constraints on the resulting algorithm.

$F$ is often explicitly chosen to be a compactly supported function. This simplifies and reduces the computational cost of the method when used in conjunction with an oct-tree based representation of $\vec{V}(\vx)$ \cite{Kazhdan06}. However, the  disadvantage of this choice is that $F$ may over smooth data in areas of high curvature \cite{reconbench}, much in the same way that a representation of a sampled signal may fail to take advantage of the full approximation power of the function space in which it is represented if it is not properly prefiltered. Theoretically, one could simply reconstruct the surface at higher resolutions, allowing the basis functions to become more ``fine'', but increasing the total amount of memory used. On a regular grid, this is undesirable. Another approach is to impose a type of ``interpolation'' constraint on the original data \cite{screenedk} \SC{section on this}.

@@

\subsection{Sampling Lattices} \label{sec:smpl_review}
In the univariate case, there is only one way to uniformly sample a signal: take equally spaced samples along the independent axis. However, when sampling multivariate signals the situation is not as straightforward. A common approach is to inherit the ideas from the univariate case and sample the function at regular intervals in each axis -- a Cartesian sampling --  while another might be to place samples at the centres of spheres arranged in the densest possible sphere packing (otherwise known as an FCC sampling). If $\mathbf{L}$ is a unimodular matrix, the set $\lattice{L} := \{\mathbf{L}\cdot\mathbf{n} : \mathbf{n} \in \intn^3 \}$ represents all possible sampling lattices. $\mathbf{L}$ is often called the \emph{generating matrix} for a lattice, and we'll assume that $\mathbf{L}$ is normalized so that $\left|\det\mathbf{L}\right| = 1$. The lattice's dual, denoted by $\duallattice{L}$, is the lattice generated by $\mathbf{L}^{-T}$. Finally, to control the sampling rate of a function a uniform scaling parameter $h$ is introduced -- lattices scaled by this parameter will be denoted by $\lattice{L}_h$. Typically, for the problem of surface reconstruction, our input data are not uniformly distributed in space, or even about the surface of the model, but the concept of a sampling lattice is fundamental in forming the definition of our target approximation spaces (\SC{sec:sis_review}).

@@

\subsection{Shift Invariant Spaces} \label{sec:sis_review}
As our target reconstruction spaces, we consider the shift-invariant spaces defined by {\small 
\begin{equation*}
	\fspce{\varphi}{ \lattice{L}_h} := \left\{ g(\vx) := \displaystyle\sum_{\mathbf{m} \in \intn^3} c[\mathbf{m}]\genfuncdef{\vx} : c \in \ell_2 \right\},
\end{equation*}}
where $\varphi$ is the generating function for the space, $h$ is a scaling parameter that controls the sampling rate or granularity, and $\mathbf{L}$ is the generating matrix for a given sampling lattice. Representing a function $f$ in a shift invariant space boils down to finding an appropriate coefficient $c[\mathbf{m}]$ vector that brings $g$ as close as possible to the true underlying function $f$.

Typically, as memory is a limited quantity, we are only interested in a finite number of points on a lattice. We denote the set of such points as $\{\mathbf{s}_1,\mathbf{s}_2,\ \hdots  \ \mathbf{s}_N\} \subset \mathbf{L}\intn^3.$ Corresponding to each lattice site is a coefficient $c_k$; we collect all such coefficients in the column vector $\mathbf{c}:=\left[c_1 \ c_2 \ \hdots \ c_N \right]^T.$ We also use the short hand notation $\varphi_k(\vx) := \varphi(\frac{\vx}{h}-\mathbf{s}_k)$; from this perspective, our function space is now {\small 
\begin{equation}
	\left\{ \displaystyle\sum_{k=0}^N c_k \varphi_k(\vx) \right\} \subset \fspce{\varphi}{\lattice{L}_h}.
\end{equation}}
Further, we denote $\mathbf{\Phii}$ to be the $M \times N$ matrix whose elements are given by sampling the basis functions anchored at each lattice site, or $P_{i,j} := \varphi_j(\vx_i)$. Clearly, if our data are sampled at the lattice sites ($\vx_i = \mathbf{s}_i$), then the problem of finding an interpolative scheme reduces to finding $\mathbf{c}$ such that $\mathbf{\Phii c=f},$ which only involves inverting the square matrix $\mathbf{\Phii}.$ However, our sample locations are almost certain to not coincide with lattice sites and we must consider alternative schemes for finding $\mathbf{c}$, which we'll come back to in \SC{sec:vari_review}

\subsection{Error Analysis} \label{sec:sis_error}
To facilitate the classical analysis of signals in a shift-invariant space, we need a few notions first. The first tool we need is the Fourier transform of a multivariate function $f(\mathbf{x})$, which we define as $\ft{f}(\vect{\omega}) := \int_{\reel^3} f(\vect{x}) \exp(-2\pi \imath
\vect{\omega} \cdot \vect{x})  \mathrm{d}\vect{x} $. The discrete time Fourier transform (DTFT) of a sequence $c[\cdot]$ associated with a lattice $\lattice{L}$ is defined as $\ft{C}(\vect{\omega}) := \sum_{\vect{m}  \in \ints^3} c[\vect{m}] \exp(-2 \pi \imath \vect{\omega} \cdot
(\mat{L}\vect{n}))$. Recall that $\ft{C}(\vect{\omega})$ is periodic with respect to the dual lattice $\duallattice{L}$, i.e. $\ft{C}(\vect{\omega} + \invtransp{\mat{L}} \vect{m}) = \ft{C}(\vect{\omega}), \forall \vect{m} \in \ints^3$. The notation `$\ftpairs{}{}$' is subsequently employed to denote transform pairs, i.e. $\ftpairs{f(\vect{x})}{\ft{f}(\vect{\omega})}$ (Fourier transform pairs) and $\ftpairs{c[\vect{m}]}{\ft{C}(\vect{\omega})}$ (DTFT pairs).

The inner product between two real valued functions $f_1$ and $f_2$ belonging to $L_2(\reel^3)$ is denoted as $\ip{f}{g} := \int_{\reel^3} f(\vect{x}) g(\vect{x}) d\vect{x}$. Likewise, the inner product between two functions $f_1$ and $f_2$ that belong to $L_2(\cube^s)$ is denoted as $\innerproduct{f_1}{f_2} := {2^{-s}} \int_{\cube^s} f_1(\vect{x}) f_2(\vect{x}) d\vect{x}$. The norms induced by these inner products are denoted as $\Ltwonorm{\cdot}$ and $\LLnorm{\cdot}$ respectively.

@@

\subsection{The Error Kernel}

The error $\Ltwonorm{f - \appf{f}}$ between $f$ and its approximation
$\appf{f} \in \aspace{\lattice{L}_h}{\varphi}$ can conveniently be
quantified via an error kernel in the Fourier domain. It is defined as
\begin{equation}
  E(\vect{\omega}) := \underbrace{1 - \frac{\abs{\ft{\varphi}(\vect{\omega})}^2}{\ft{A}_{\varphi}(\vect{\omega})}}_{E_{\mathsf{min}}(\vect{\omega})}
  + 
  \underbrace{
    \ft{A}_{\varphi}(\vect{\omega})
    \abs{\ft{\analysis{\varphi}}(\vect{\omega}) -
      \ft{\dual{\varphi}}(\vect{\omega})}^2
  }_{E_{\mathsf{res}}(\vect{\omega})}.
  \label{eq:scErrorKernel}
\end{equation}
For a bandlimited function $f$ whose spectrum is entirely contained
within the Voronoi cell of $\duallattice{L}_h$ centered around
$\vect{\omega} = 0$, we have 
\begin{equation}
\Ltwonorm{f - \appf{f}} = \int_{\reel^s}
\abs{\ft{f}(\vect{\omega})}^2 E(h\vect{\omega}) d\vect{\omega},
\label{eq:avgError}
\end{equation}
whereas when $f \in W_2^k(\reel^s)$ with $k > \frac{1}{2}$, the
integral in~\eqref{eq:avgError} gives the $L_2$-error averaged over
all possible shifts of $f$. Even though this kernel was initially
proposed in the univariate setting by Blu and Unser~\cite{blu99}, multivariate
non-Cartesian extensions have also appeared in the
literature~\cite{condat05hexagonal, condat07, condat08, alim10,
  condat11}. Note that the minimum-error approximation scenario occurs
when $f$ is orthogonally projected to $\aspace{\lattice{L}_h}{\varphi}$,
or in other words $\analysis{\varphi}$ is chosen to be  $\dual{\varphi}$.
 polynomial spaces,

>>>>

\section{Preliminaries}\label{sec:pois_review}
\subsection{Poisson Surface Reconstruction}
We denote the indicator function of a model $M$ as $$ \chi_M(\vect{x}) :=
\begin{cases}
1, & \text{if }\vect{x}\text{ is in the interior of the model } M \\
\frac{1}{2}, & \text{if } \vect{x}\text{ is on the model's surface}\\
0, & \text{if }\vect{x}\text{ is exterior to } M
\end{cases}. $$
The key observation of the Poisson surface reconstruction formulation, is that if one obtains a function $\vec{V}(\vect{x})$ with $\vec{V}(\vect{x})\approx{\nabla}\chi_M$, that approximates the smoothed gradient of the indicator function, finding an approximation to the indicator function reduces to finding a $\inda$ such that {\small 
\begin{equation} \label{eq:poisson}
	\lapl{\inda} = {\grad} \cdot \vec{V}.
\end{equation}}
We define the set of input surface points to be $P:=\{(\vect{p}_1,\vect{n}_1), (\vect{p}_2,\vect{n}_2) \hdots (\vect{p}_M,\vect{n}_M) : (\vect{p}_i,\vect{n}_i) \in \realn^3 \times \realn^3 \}$ where $\vect{p}_i$ and $\mathbf{n}_i$ are the position and normal vector of the $i^{th}$ sample respectively. Orientation can be succinctly represented with only two values, however, it is convenient to keep it as the normal at a point, because the length of the normal can be used to encode the sampling density of the point-set at a point. For the following discussion, we also need to introduce the notation $\patch_{\vect{s}}$, which denotes a patch of the surface model about the sample location $\vect{s}$.

Inspired by the approach of Kazhdan et al.~\cite{Kazhdan06} the approximation $\vec{V}(\vx)$ is defined to be  {\small 
\begin{eqnarray}
	\vec{V}(\vx) & := & \sum_{(\vect{s},\vect{n}) \in P}\left|\patch_s\right|F(\vx-\vect{s})\cdot\vn \label{eq:vdef} \\
	 & \approx & \sum_{(\vect{s},\vect{n}) \in P} \int_{\patch_s}{F(\vect{x} - \vect{p}) \nabla \chi (\vect{p})} \mathrm{d} \vect{p}. \notag  
\end{eqnarray}}
Thus, $\vec{V}(\vx)$ approximates the gradient of the indicator smoothed by some filter $F$, broken up over surface patches of the model. We assume the point sampling to be uniform, thus the area of each patch $\left|\patch_s\right|$ should be a constant, and our resulting approximation will be scaled by an unknown factor. We return to this in \SC{sec:levelset}. The choice of $F$ places computational constraints on the resulting algorithm.

$F$ is often explicitly chosen to be a compactly supported function. This simplifies and reduces the computational cost of the method when used in conjunction with an oct-tree based representation of $\vec{V}(\vx)$ \cite{Kazhdan06}. However, the  disadvantage of this choice is that $F$ may over smooth data in areas of high curvature \cite{reconbench}, much in the same way that a representation of a sampled signal may fail to take advantage of the full approximation power of the function space in which it is represented if it is not properly prefiltered. Theoretically, one could simply reconstruct the surface at higher resolutions, allowing the basis functions to become more ``fine'', but increasing the total amount of memory used. On a regular grid, this is undesirable. Another approach is to impose a type of ``interpolation'' constraint on the original data \cite{screenedk} (\SC{sec:vari_review}).

@@

\subsection{Sampling Lattices} \label{sec:smpl_review}
In the univariate case, there is only one way to uniformly sample a signal: take equally spaced samples along the independent axis. However, when sampling multivariate signals the situation is not as straightforward. A common approach is to inherit the ideas from the univariate case and sample the function at regular intervals in each axis -- a Cartesian sampling --  while another might be to place samples at the centres of spheres arranged in the densest possible sphere packing (otherwise known as an FCC sampling). If $\mathbf{L}$ is a unimodular matrix, the set $\lattice{L} := \{\mathbf{L}\cdot\vect{n} : \vect{n} \in \intn^3 \}$ represents all possible sampling lattices. $\mathbf{L}$ is often called the \emph{generating matrix} for a lattice, and we'll assume that $\mathbf{L}$ is normalized so that $\left|\det\mathbf{L}\right| = 1$. The lattice's dual, denoted by $\duallattice{L}$, is the lattice generated by $\mathbf{L}^{-T}$. Finally, to control the sampling rate of a function a uniform scaling parameter $h$ is introduced -- lattices scaled by this parameter will be denoted by $\lattice{L}_h$. Typically, for the problem of surface reconstruction, our input data are not uniformly distributed in space, or even about the surface of the model, but the concept of a sampling lattice is fundamental in forming the definition of our target approximation spaces (\SC{sec:sis_review}).

@@

\subsection{Shift Invariant Spaces} \label{sec:sis_review}
As our target reconstruction spaces, we consider the shift-invariant spaces defined by {\small 
\begin{equation*}
	\fspce{\varphi}{ \lattice{L}_h} := \left\{ g(\vx) := \displaystyle\sum_{\vect{m} \in \intn^3} c[\vect{m}]\genfuncdef{\vx} : c \in \ell_2 \right\},
\end{equation*}}
where $\varphi$ is the generating function for the space, $h$ is a scaling parameter that controls the sampling rate or granularity, and $\mathbf{L}$ is the generating matrix for a given sampling lattice. Representing a function $f$ in a shift invariant space boils down to finding an appropriate coefficient $c[\vect{m}]$ vector that brings $g$ as close as possible to the true underlying function $f$.

Typically, as memory is a limited quantity, we are only interested in a finite number of points on a lattice. We denote the set of such points as $\{\vect{s}_1,\vect{s}_2,\ \hdots  \ \vect{s}_N\} \subset \mathbf{L}\intn^3.$ Corresponding to each lattice site is a coefficient $c_k$; we collect all such coefficients in the column vector $\mathbf{c}:=\left[c_1 \ c_2 \ \hdots \ c_N \right]^T.$ We also use the short hand notation $\varphi_k(\vx) := \varphi(\frac{\vx}{h}-\vect{s}_k)$; from this perspective, our function space is now {\small 
\begin{equation}
	\left\{ \displaystyle\sum_{k=0}^N c_k \varphi_k(\vx) \right\} \subset \fspce{\varphi}{\lattice{L}_h}.
\end{equation}}
Further, we denote $\mathbf{\Phii}$ to be the $M \times N$ matrix whose elements are given by sampling the basis functions anchored at each lattice site, or $P_{i,j} := \varphi_j(\vx_i)$. Clearly, if our data are sampled at the lattice sites ($\vx_i = \vect{s}_i$), then the problem of finding an interpolative scheme reduces to finding $\vect{c}$ such that $\mathbf{\Phii c=f},$ which only involves inverting the square matrix $\mathbf{\Phii}.$ However, our sample locations are almost certain to not coincide with lattice sites and we must consider alternative schemes for finding $\mathbf{c}$, which we'll come back to in \SC{sec:vari_review}

\subsection{Error Analysis} \label{sec:sis_error}
To facilitate the classical analysis of signals in a shift-invariant space, we need a few notions first. We define all this notation in $s$-dimensions, as the generalization comes at little cost. The first tool we need is the Fourier transform of a multivariate function $f(\vect{x})$, which we define as $ \ft{f}(\vect{\omega}) := \int_{\reel^s} f(\vect{x}) \exp(-2\pi \imath \vect{\omega} \cdot \vect{x}) \mathrm{d}\vect{x} $. The discrete time Fourier transform (DTFT) of a sequence $c[\cdot]$ associated with a lattice $\lattice{L}$ is defined as $\ft{C}(\vect{\omega}) := \sum_{\vect{m}  \in \ints^s} c[\vect{m}] \exp(-2 \pi \imath \vect{\omega} \cdot (\mat{L}\vect{n}))$. Recall that $\ft{C}(\vect{\omega})$ is periodic with respect to the dual lattice $\duallattice{L}$, i.e. $\ft{C}(\vect{\omega} + \invtransp{\mat{L}} \vect{m}) = \ft{C}(\vect{\omega}), \forall \vect{m} \in \ints^s$. The notation `$\ftpairs{}{}$' is subsequently employed to denote transform pairs, i.e. $\ftpairs{f(\vect{x})}{\ft{f}(\vect{\omega})}$ (Fourier transform pairs) and $\ftpairs{c[\vect{m}]}{\ft{C}(\vect{\omega})}$ (DTFT pairs).

The closed unit hypercube $[0,1]^s$ is denoted as $\ucube^s$ while the closed hypercube $[-1,1]^s$ is denoted as $\cube^s$. The corresponding open hypercubes are denoted as $\oucube^s$ and $\ocube^s$ respectively. The inner product between two real valued functions $f_1$ and $f_2$ belonging to $L_2(\reel^s)$ is denoted as $\ip{f}{g} := \int_{\reel^s} f(\vect{x}) g(\vect{x}) d\vect{x}$. Likewise, the inner product between two functions $f_1$ and $f_2$ that belong to $L_2(\cube^s)$ is denoted as $\innerproduct{f_1}{f_2} := {2^{-s}} \int_{\cube^s} f_1(\vect{x}) f_2(\vect{x}) d\vect{x}$. The norms induced by these inner products are denoted as $\Ltwonorm{\cdot}$ and $\LLnorm{\cdot}$ respectively.

@@

\subsection{The Error Kernel}
The error $\Ltwonorm{f - \appf{f}}$ between $f$ and its approximation
$\appf{f} \in \aspace{\lattice{L}_h}{\varphi}$ can conveniently be
quantified via an error kernel in the Fourier domain. It is defined as
\begin{equation}
	E(\vect{\omega}) := \underbrace{1 - \frac{\abs{\ft{\varphi}(\vect{\omega})}^2}{\ft{A}_{\varphi}(\vect{\omega})}}_{E_{\mathsf{min}}(\vect{\omega})}
	+ 
	\underbrace{
	\ft{A}_{\varphi}(\vect{\omega})
	\abs{\ft{\analysis{\varphi}}(\vect{\omega}) -
 		\ft{\dual{\varphi}}(\vect{\omega})}^2
  	}_{E_{\mathsf{res}}(\vect{\omega})}.
  \label{eq:scErrorKernel}
\end{equation}
For a bandlimited function $f$ whose spectrum is entirely contained
within the Voronoi cell of $\duallattice{L}_h$ centered around $\vect{\omega} = 0$, we have 
\begin{equation}
	\Ltwonorm{f - \appf{f}} = \int_{\reel^s}
	\abs{\ft{f}(\vect{\omega})}^2 E(h\vect{\omega}) d\vect{\omega},
	\label{eq:avgError}
\end{equation}
whereas when $f \in W_2^k(\reel^s)$ with $k > \frac{1}{2}$, the integral in~\eqref{eq:avgError} gives the $L_2$-error averaged over all possible shifts of $f$. Even though this kernel was initially proposed in the univariate setting by Blu and Unser~\cite{blu99}, multivariate non-Cartesian extensions have also appeared in the literature~\cite{condat05hexagonal, condat07, condat08, alim10, condat11}. Note that the minimum-error approximation scenario occurs when $f$ is orthogonally projected to $\aspace{\lattice{L}_h}{\varphi}$, or in other words $\analysis{\varphi}$ is chosen to be $\dual{\varphi}$.
